---
title: "Shiny Project: NZ Migration"
author: "Sita Thomas"
date: "4/27/2020"
output: html_document
---

```{r setup, include=F}
knitr::opts_chunk$set(echo = TRUE)

library(readr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(ggthemes)
library(scales)

```


## Data Information

Data can be downloaded at: http://archive.stats.govt.nz/infoshare/  
Subject Categories > Tourism > International Travel and Migration

```{r preprocessing, include=F}

major_occup <- read_csv("data/major_occupations.csv", col_names = T, skip = 3)
major_occup <- major_occup[-(9:44),]
colnames(major_occup)[1] = "year"
colnames(major_occup) <- gsub("and", "", colnames(major_occup))
colnames(major_occup) <- gsub(" ", "_", colnames(major_occup))
colnames(major_occup) <- tolower(colnames(major_occup))
colnames(major_occup)[13] = "total_occupations"

by_gender <-
	read_csv("data/arrivals_by_gender.csv", col_names = T, skip = 4)
by_gender <- by_gender[-(9:41),]
colnames(by_gender)[1] = "year"
females <- by_gender %>%
	pivot_longer(., 2:7, names_to = "visa_type", values_to = "females") %>%
	select(., year, visa_type, females)
males <- by_gender %>%
	pivot_longer(., 8:13, names_to = "visa_type", values_to = "males") %>%
	select(., year, visa_type, males) %>%
	mutate(., visa_type = gsub("_1", "", visa_type))
by_gender <- inner_join(females, males, by = c("year", "visa_type")) %>% 
	pivot_longer(., c(females, males), names_to = "gender", values_to = "arrivals")

by_age <-
	read_csv("data/arrivals_by_age.csv", col_names = T, skip = 4)
by_age <- by_age[-(9:41),]
colnames(by_age)[1] = "year"
age_0_4 <- by_age %>%
	pivot_longer(., 2:7, names_to = "visa_type", values_to = "age_0_4") %>%
	select(., year, visa_type, age_0_4)
age_5_9 <- by_age %>%
	pivot_longer(., 8:13, names_to = "visa_type", values_to = "age_5_9") %>%
	select(., year, visa_type, age_5_9) %>%
	mutate(., visa_type = gsub("_1", "", visa_type))
age_10_14 <- by_age %>%
	pivot_longer(., 14:19, names_to = "visa_type", values_to = "age_10_14") %>%
	select(., year, visa_type, age_10_14) %>%
	mutate(., visa_type = gsub("_2", "", visa_type))
age_15_19 <- by_age %>%
	pivot_longer(., 20:25, names_to = "visa_type", values_to = "age_15_19") %>%
	select(., year, visa_type, age_15_19) %>%
	mutate(., visa_type = gsub("_3", "", visa_type))
age_20_24 <- by_age %>%
	pivot_longer(., 26:31, names_to = "visa_type", values_to = "age_20_24") %>%
	select(., year, visa_type, age_20_24) %>%
	mutate(., visa_type = gsub("_4", "", visa_type))
age_25_29 <- by_age %>%
	pivot_longer(., 32:37, names_to = "visa_type", values_to = "age_25_29") %>%
	select(., year, visa_type, age_25_29) %>%
	mutate(., visa_type = gsub("_5", "", visa_type))
age_30_34 <- by_age %>%
	pivot_longer(., 38:43, names_to = "visa_type", values_to = "age_30_34") %>%
	select(., year, visa_type, age_30_34) %>%
	mutate(., visa_type = gsub("_6", "", visa_type))
age_35_39 <- by_age %>%
	pivot_longer(., 44:49, names_to = "visa_type", values_to = "age_35_39") %>%
	select(., year, visa_type, age_35_39) %>%
	mutate(., visa_type = gsub("_7", "", visa_type))
age_40_44 <- by_age %>%
	pivot_longer(., 50:55, names_to = "visa_type", values_to = "age_40_44") %>%
	select(., year, visa_type, age_40_44) %>%
	mutate(., visa_type = gsub("_8", "", visa_type))
age_45_49 <- by_age %>%
	pivot_longer(., 56:61, names_to = "visa_type", values_to = "age_45_49") %>%
	select(., year, visa_type, age_45_49) %>%
	mutate(., visa_type = gsub("_9", "", visa_type))
age_50_54 <- by_age %>%
	pivot_longer(., 62:67, names_to = "visa_type", values_to = "age_50_54") %>%
	select(., year, visa_type, age_50_54) %>%
	mutate(., visa_type = gsub("_10", "", visa_type))
age_55_59 <- by_age %>%
	pivot_longer(., 68:73, names_to = "visa_type", values_to = "age_55_59") %>%
	select(., year, visa_type, age_55_59) %>%
	mutate(., visa_type = gsub("_11", "", visa_type))
age_60_64 <- by_age %>%
	pivot_longer(., 74:79, names_to = "visa_type", values_to = "age_60_64") %>%
	select(., year, visa_type, age_60_64) %>%
	mutate(., visa_type = gsub("_12", "", visa_type))
age_65_69 <- by_age %>%
	pivot_longer(., 80:85, names_to = "visa_type", values_to = "age_65_69") %>%
	select(., year, visa_type, age_65_69) %>%
	mutate(., visa_type = gsub("_13", "", visa_type))
age_70_74 <- by_age %>%
	pivot_longer(., 86:91, names_to = "visa_type", values_to = "age_70_74") %>%
	select(., year, visa_type, age_70_74) %>%
	mutate(., visa_type = gsub("_14", "", visa_type))
age_75_up <- by_age %>%
	pivot_longer(., 92:97, names_to = "visa_type", values_to = "age_75_up") %>%
	select(., year, visa_type, age_75_up) %>%
	mutate(., visa_type = gsub("_15", "", visa_type))
by_age <-
	inner_join(age_0_4, age_5_9, by = c("year", "visa_type")) %>%
	inner_join(age_10_14, age_15_19, by = c("year", "visa_type")) %>%
	inner_join(age_20_24, age_25_29, by = c("year", "visa_type")) %>%
	inner_join(age_30_34, age_35_39, by = c("year", "visa_type")) %>%
	inner_join(age_40_44, age_45_49, by = c("year", "visa_type")) %>%
	inner_join(age_50_54, age_55_59, by = c("year", "visa_type")) %>%
	inner_join(age_60_64, age_65_69, by = c("year", "visa_type")) %>%
	inner_join(age_70_74, age_75_up, by = c("year", "visa_type"))


# by_age <- by_age %>% 
# 	pivot_longer(., c(
# 		age_0_4, age_5_9, age_10_14, age_15_19,
# 		age_20_24, age_25_29, age_30_34, age_35_39,
# 		age_40_44, age_45_49, age_50_54, age_55_59,
# 		age_60_64, age_65_69, age_70_74, age_75_up
# 		),
# 		names_to = "age",
# 		values_to = "arrivals"
# 	)


```

## Exploring Net Permanent and Long-Term Migration by Year

```{r by_year, echo = F}

major_occup %>% 
	group_by(year) %>% 
	summarise(., total = sum(total_occupations)) %>% 
	ggplot(., aes(x = year, y = total)) +
		geom_col(fill = "sienna3") +
		labs(
			title = "Net Permanent and Long-Term Migration to New Zealand by Year",
			subtitle = "ANZSCO Major Occupations, 2010 - 2017",
			x = "Year", y = "All Major ANZSCO Occupations") +
		theme_few()

```


#### Conclusion: Exploring Net Permanent and Long-Term Migration by Year
- Although fairly level in 2016 and 2017, permanent and long-term migration to New Zealand for workers in the ANZSCO Major Occupation groups has increased throughout the 2010s.

## Exploring Net Migration by Occupation

```{r by_occupation, echo = F}

major_occup %>% 
	pivot_longer(.,
		cols = managers:labourers,
		names_to = "occupation",
		values_to = "occupation_count"
	) %>% 
	group_by(., occupation) %>% 
	summarise(., occupation_sum = sum(occupation_count)) %>% 
	ggplot(data = ., aes(y = occupation, x = occupation_sum)) +
		geom_col(fill = "sienna3") +
		labs(
			title = "Net Permanent and Long-Term Migration to New Zealand by Occupation",
			subtitle = "ANZSCO Major Occupations, 2010 - 2017",
			y = "Occupation", x = "All Major ANZSCO Occupations"
			) +
		theme_few() +
		scale_y_discrete(
			labels = c(
				"technicians__trades_workers" = "Technicians and Trades Workers",
				"sales_workers" = "Sales Workers",
				"professionals" = "Professionals",
				"managers" = "Managers",
				"machinery_operators__drivers" = "Machinery Operators and Drivers",
				"labourers" = "Laborers",
				"community__personal_service_workers" = "Community and Personal Service Workers",
				"clerical__administrative_workers" = "Clerical and Administrative Workers"
			)
		)

```


#### Conclusion: Exploring Net Permanent and Long-Term Migration by Occupation
- Most permanent and long-term migrants are Professionals by far, while more Sales Workers and Machinery Operators and Drivers have departed New Zealand than have arrived.

```{r by_gender, echo = F}

ggplot(by_gender, aes(x = arrivals, y = visa_type, fill = gender)) +
	geom_col(position = "dodge") +
	facet_wrap(. ~ year) # SLIDER MENU FOR R SHINY?

ggplot(by_gender, aes(x = year, y = arrivals, fill = gender)) +
	geom_col(position = "dodge")

```

