---
title: "Shiny Project: NZ Migration"
author: "Sita Thomas"
date: "4/27/2020"
output: html_document
---

```{r setup, include=F}
knitr::opts_chunk$set(echo = TRUE)

library(readr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(ggthemes)

```

## Data Preparation

Data can be downloaded at: http://archive.stats.govt.nz/infoshare/  
Subject Categories > Tourism > International Travel and Migration

```{r preprocessing, include=F}

raw <- read_csv("data/ITM359302_20200428_125710_33.csv", col_names = T, skip = 3)
View(raw)

colnames(raw)[1] = "year"
	
data <- 
	separate(raw, year, c("year", "quarter"), sep = "Q") %>% 
	.[-c(33:68),]
View(data)
	
```

## Exploring Permanent and Long-Term Migration by Year

```{r}

data %>% 
	group_by(year) %>% 
	summarise(., total_occupations = sum(`TOTAL ALL ANZSCO OCCUPATIONS (MAJOR)`)) %>% 
	ggplot(., aes(x = year, y = total_occupations)) +
		geom_bar(stat = "identity", fill = "sienna3") +
		labs(title = "Permanent and Long-Term Migration to New Zealand by Year",
			subtitle = "ANZSCO Major Occupations, 2010 - 2017",
			x = "Year", y = "All Major ANZSCO Occupations") +
		theme_few()

```


## Conclusion: Exploring Permanent and Long-Term Migration by Year
- Although fairly level in 2016 and 2017, permanent and long-term migration to New Zealand for workers in the ANZSCO Major Occupation groups has increased throughout the 2010s.

```{r}



```

